---
title: "MUSA_Final"
author: "Richard Barad"
date: "2023-12-04"
output: html_document
---

```{r clear_environment, include=FALSE}

# Lists All Of The Objects In The Work Space
rm(list=ls())
```

```{r knitting_options, include = FALSE}
# Global Options For Knitting Chunks
knitr::opts_chunk$set(echo = T, messages = F, warning = F, error = F)
```

```{r import_libraries, include = FALSE}
library(tidyverse) # Data Science Workflow & Representation
library(tidycensus) # Load United States Census Boundary & Attribute Data
library(sf) # Standardized Way To Encode Spatial Vector Data
library(spdep) # Spatial Dependence: Weighting Schemes & Statistics
library(caret) # Classification and Regression Training
library(FNN) # Fast Nearest Neighbor Search Algorithms & Applications
library(RSocrata) # Download or Upload 'Socrata' Data Sets/Open Data Portals
library(viridis) # Colorblind-Friendly Color Maps Package
library(gridExtra) # Miscellaneous Functions for "Grid" Graphics
library(knitr) # General-Purpose Package for Dynamic Report Generation
library(kableExtra) # Construct Complex Table with 'Kable' and Pipe Syntax
library(plotROC) # Generate Useful ROC Curve Charts for Print and Interactive Use
library(pROC) # Display and Analyze Receiver Operating Characteristic Curves
library(lubridate) # Functions to Work with Date-Times and Time-Spans
library(ggpubr) # GGPLOT Based Publication Ready Plots
library(matchmaker)
library(corrr) #For correlation Matrix
library(RColorBrewer)
library(ROCR)

# functions
root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")
```

## Read the data using the Socrata API

I filtered to just restaurants and converted data to an SF object


```{r read_data, cache=TRUE}

#Read data from city of Chicago on inspections - we need all data is read in (we need all data since we look at historical failures)

data <- read.socrata("https://data.cityofchicago.org/Health-Human-Services/Food-Inspections/4ijn-s7e5") %>%
  na.omit() %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326, agr = "constant") %>%
  mutate(inspection_date = ymd(inspection_date),
         year = year(inspection_date),
         month = month(inspection_date),
         address = str_squish(address)) %>%
  st_transform('ESRI:102271') %>%
  mutate(facility_type = str_squish(str_to_title(facility_type)))

#Clean up a bunch of messy facility names to be able to identify just facilities of (i.e: restaurants, cafes,and bakeries)

data$facility_type[grepl("Restaurant", data$facility_type)] <- "Restaurant"
data$facility_type[grepl("Bakery", data$facility_type)] <- "Bakery"
data$facility_type[grepl("Coffee", data$facility_type)] <- "Coffee Shop"
data$facility_type[grepl("Ice Cream", data$facility_type)] <- "Ice Cream Shop"
data$facility_type[grepl("Deli", data$facility_type)] <- "Deli"
data$facility_type[grepl("Taqueria", data$facility_type)] <- "Restaurant"
data$facility_type[grepl("Hot Dog Station", data$facility_type)] <- "Restaurant"
data$facility_type[grepl("Juice and Salad Bar", data$facility_type)] <- "Restaurant"

#Standardize some names of bussinesses

data$dba_name[grepl("SEE THRU CHINESE", data$dba_name)] <- 'SEE THRU CHINESE RESTAURANT'
data$dba_name[grepl("JAMAICAN  GATES", data$dba_name)] <- 'JAMAICAN GATES'
```

## Read Neighboorhoods Data

```{r neighboorhoods_data}

neighboorhoods <- st_read('https://data.cityofchicago.org/api/geospatial/bbvz-uum9?method=export&format=GeoJSON')%>%
  st_transform('ESRI:102271') %>%
  dplyr::select(pri_neigh)

```


I figured our training data would be one year of data - this is 9,185 data points. I also removed all results which were not Pass or Fail. Also filtered to just restaurants which are the type of bussinesses we are interested in. 

```{r training_data}

filter <- c("Restaurant","Bakery","Tavern","Ice Cream Shop","Deli","Cafe","Coffee Shop","")

data_2021 <- data %>%
  dplyr::filter(year == 2021 & results != 'Out of Business' & results != 'No Entry' & results != 'Not Ready') %>%
  dplyr::filter(facility_type %in% filter) %>%
  mutate(results = ifelse(results=="Pass w/ Conditions","Pass",results),
         fail = ifelse(results=="Fail",1,0)) %>%
  st_join(.,neighboorhoods,predicate = st_intersects) %>%
  mutate(pri_neigh = ifelse(location == "(42.008536400868735, -87.91442843927047)","O'Hare",pri_neigh),
         pri_neigh = ifelse(location %in% c("(41.892249163400116, -87.60951804879336)","(41.89233780863412, -87.6040447589981)"),"Streeterville",pri_neigh)) %>%
  dplyr::filter(pri_neigh != "O'Hare")

```

## Try to estimate bussiness age

Download all bussiness liscences going back to 2010.

```{r download_liscenses, cache=TRUE}

#Download all liscences data since 2010, started in 2010 because inspection data does not go back more than 10 years

liscenses <- read.socrata("https://data.cityofchicago.org/resource/r5kz-chrr.json?$where=license_start_date%20between%20%272010-01-01T12:00:00%27%20and%20%272021-12-31T14:00:00%27")

```

This code is all cleaning the bussiness liscence data, to ensure that addresses match across the bussiness liscence data and inspections data since we join the two together. Matching on the liscence_id often did not work!

```{r clean_data}

#Doing some manual cleaning of address

corrections <- data.frame(
  bad = c("4623-4627 N BROADWAY  1 & 2","100 E WALTON ST 1 104","436-440 E 79TH ST","1733 W 87TH ST 1ST FLOOR","163 E WALTON ST 2ND F","5640 S UNIVERSITY AVE","5255 W MADISON ST 1 B","111 E 51ST ST 1ST`"),
  good = c("4623-4627 N BROADWAY", "100 E WALTON ST","436 - 440 E 79TH ST","1733 W 87TH ST","163 E WALTON ST","5640 S UNIVERSITY","5255 W MADISON ST","111 E 51ST ST 1ST"),
  stringsAsFactors = FALSE
)

liscenses$address <- match_vec(x=liscenses$address,corrections,from=1,to=2, quiet=TRUE)

liscenses$address[grepl("47 W POLK ST", liscenses$address)] <- "47 W POLK ST"

liscenses$address <- gsub("\\s*\\d+$", "", liscenses$address) #Remove any trailing numbers

liscenses$address <- gsub("\\s*\\d+(ST)?$", "", liscenses$address) #Remove any trailing numbers which are followed by ST

liscenses$address <- gsub("\\s*\\d+(st)?$", "", liscenses$address) #Remove any trailing numbers which are followed by st

#Standardize some business names

liscenses$doing_business_as_name[grepl("SEE THRU CHINESE", liscenses$doing_business_as_name)] <- 'SEE THRU CHINESE RESTAURANT'
liscenses$doing_business_as_name[grepl("THE NEW VALOIS REST", liscenses$doing_business_as_name)] <- 'THE NEW VALOIS REST INC'
liscenses$doing_business_as_name[grepl("CHICAGO MARRIOTT DOWNTOWN", liscenses$doing_business_as_name)] <- 'CHICAGO DOWNTOWN MARRIOTT'
liscenses$doing_business_as_name[grepl("STAR OF SIAM", liscenses$doing_business_as_name)] <- 'STAR OF SIAM'
liscenses$doing_business_as_name[grepl("EL CHILE RESTAURANT & PANCAKE HOUSE.", liscenses$doing_business_as_name)] <- 'EL CHILE RESTAURANT & PANCAKE HOUSE'
liscenses$doing_business_as_name[grepl("FRANCES' DELI & BRUNCHERY", liscenses$doing_business_as_name)] <- "FRANCES' REST & BRUNCHERY"

```

This code determines the age of each business, based on what the business requested it first business liscence. Age is estiamted in days - max age should be around 365 * 11 since we only downloaded liscence data back to 2010 (11 years because we only focus on 2010).

``` {r determine_age}
#For each for retail establishment determine date when a license was first obtained
liscense_min <- liscenses %>% group_by(doing_business_as_name,address) %>% summarize(min_date = min(license_start_date)) %>%
  arrange(min_date)

#Join min date back to original licence data and select subset of columns 

liscenses_final <- left_join(liscenses, liscense_min , by = c('doing_business_as_name','address')) %>%
  select(license_id, account_number,legal_name,doing_business_as_name,address,site_number,min_date) %>%
  mutate(license_id = as.integer(license_id))

#Join date business applied for first licence to 2021 inspection data - try to joins a variety of different ways since joining on licence number did not match allways

data_2021_2 <- left_join(data_2021,liscenses_final %>% select(license_id,min_date),by=join_by(license_==license_id)) %>%
  rename(min_date1 = 'min_date') %>%
  left_join(.,liscense_min %>% select(doing_business_as_name,address,min_date),by=join_by(dba_name==doing_business_as_name,address==address),multiple='first') %>%
  rename(min_date2 = 'min_date') %>%
  left_join(.,liscense_min %>% select(doing_business_as_name,address,min_date),by=join_by(aka_name==doing_business_as_name,address==address),multiple='first') %>%
  rename(min_date3 = 'min_date') %>%
  mutate(min_date = pmin(min_date1, min_date2, min_date3, na.rm = TRUE), #Select lowest date where multiple joins worked
         age = as.integer(difftime(inspection_date, min_date, units = 'days')))

data_2021_2 <- data_2021_2 %>%
  mutate(age = ifelse(age<0,0,age),
         age = ifelse(is.na(age),median(age,na.rm=TRUE),age))
  
```

## Estimate Number of previous violations and join

This code estimates the number of previous violations at each bussiness.

```{r estimate_failures}

fails <- data %>%
  st_drop_geometry() %>%
  dplyr::filter(year<2021 & results == 'Fail') %>%
  group_by(dba_name,address) %>% tally() %>%
  ungroup() %>%
  rename(prev_fails = 'n')

data_2021_2 <- left_join(data_2021_2,fails,by=join_by(dba_name==dba_name,address==address)) %>%
  mutate(prev_fails = replace_na(prev_fails,0),
         fails_Per_year = replace_na(prev_fails/(age/365),0),
         fails_Per_year =  ifelse(is.infinite(fails_Per_year), prev_fails, fails_Per_year))

```

## Census Wrangling

Wrangle and download census data on percent white population, percent poverty, and median rent by census block.

```{r census_data, results = 'hide'}
variables = c("B17017_002", #Total Households w/ income below poverty line
              "B17017_001", #Total Households 
              "B02001_001", #Total Population
               "B02001_002", #Total White Population
               "B25058_001") #Median Rent

census_data <- get_acs("block group",
        year=2021,
        output='wide',
        geometry=T,
        variables = variables,
        state = 'IL',
        county = 'Cook'
        ) %>%
  st_transform('ESRI:102271') %>%
  select(ends_with('E'),'GEOID') %>%
  rename(poverty = "B17017_001E",
         below_poverty_line = "B17017_002E",
         Total_Population = "B02001_001E",
         White_Population = "B02001_002E",
         Median_Rent = "B25058_001E") %>%
  mutate(Median_Rent = ifelse(is.na(Median_Rent),median(Median_Rent,na.rm=TRUE),Median_Rent),
         pct_non_white = 100 - ifelse(Total_Population == 0,0,White_Population / Total_Population * 100),
         pct_poverty = ifelse(poverty == 0,0, below_poverty_line / poverty * 100)) %>%
  select('Median_Rent','pct_non_white','pct_poverty','GEOID')
```

Spatial join census data to restaurants data

```{r join_censu_data}
data_2021_2 <- data_2021_2 %>%
  st_join(.,census_data,predicate = st_intersects)

means_neigh <- data_2021_2 %>% 
  st_drop_geometry() %>% 
  group_by(pri_neigh) %>% summarize_at(vars("pct_poverty","Median_Rent","pct_non_white"),mean,na.rm=TRUE)

data_2021_2 <- left_join(data_2021_2,means_neigh,by='pri_neigh') %>%
  mutate(pct_poverty = ifelse(is.na(pct_poverty.x),pct_poverty.y,pct_poverty.x),
         Median_Rent = ifelse(is.na(Median_Rent.x),Median_Rent.y,Median_Rent.x),
         pct_non_white = ifelse(is.na(pct_non_white.x),pct_non_white.y,pct_non_white.x)) %>%
  select(-ends_with('.x'),-ends_with('.y'))

```

## Including Plots

Quick Map 1

```{r guick_map1}


custom_colors <- c("Pass" = "#41B6E6", "Fail" = "#E4002B")

ggplot() +
  geom_sf(data = neighboorhoods) +
  geom_sf(data = data_2021, aes(color = results), size = 0.5) +
  scale_color_manual(values = custom_colors) +
  theme_void()

```

```{r guick_map2}
neigh_summ <- data_2021 %>% st_drop_geometry() %>%
  group_by(pri_neigh,results) %>% tally() %>%
  spread(key=results,value=n) %>%
  mutate(Fail = replace_na(Fail,0),
    pct_pass = Pass / (Fail + Pass) * 100,
    pct_fail = Fail / (Fail + Pass) * 100)%>%
  left_join(neighboorhoods,.,by='pri_neigh') 
  
ggplot() +
  geom_sf(data = neigh_summ, aes(fill = pct_pass)) +
  scale_fill_distiller(palette = "Blues") +
  theme_void()
```

```{r guick_chart, fig.width=14}

neigh_summ %>% 
  st_drop_geometry() %>%
  select(pri_neigh,pct_pass,pct_fail) %>%
  gather(pass,rate,-pri_neigh) %>%
  na.omit() %>%
  ggplot(aes(x=pri_neigh,y=rate,fill=pass))+
  geom_bar(position='stack',stat='identity')+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# Alec's Code Begins Here

```{r chicago_boundary}

chicagoboundary <- 
  st_read("https://data.cityofchicago.org/api/geospatial/ewy2-6yfk?method=export&format=GeoJSON") %>%
  st_transform('ESRI:102271')

```
```{r get_lots_311, cache=TRUE}

sanitation <- read.socrata("https://data.cityofchicago.org/resource/v6vf-nfxy.json?SR_SHORT_CODE='SCB'")
rodents <- read.socrata("https://data.cityofchicago.org/resource/v6vf-nfxy.json?SR_SHORT_CODE='SGA'")
bussiness_complaint <- read.socrata("https://data.cityofchicago.org/resource/v6vf-nfxy.json?SR_SHORT_CODE='RBL'")

clean_311 <- function(df){
  clean_df <- df %>%
  mutate(created_date = ymd_hms(created_date),
         year = year(created_date)) %>%
  dplyr::filter(year == 2020 & duplicate=='FALSE') %>%
  dplyr::filter(!is.na(longitude)) %>%
  dplyr::filter(!is.na(latitude)) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102271')
  return(clean_df)
}

sanitation2 <- clean_311(sanitation)
rodents2 <- clean_311(rodents)
bussiness_complaint2 <- clean_311(bussiness_complaint)
```

``` {r read_crime}
thefts <- read.socrata('https://data.cityofchicago.org/resource/qzdf-xmn8.json?primary_type=THEFT') %>%
  mutate(created_date = ymd_hms(date),
         year = year(date)) %>%
  dplyr::filter(!is.na(longitude)) %>%
  dplyr::filter(!is.na(latitude)) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102271')
```

```{r complaints_visualized, fig.width=9.5, fig.height=4}

grid.arrange(
  ncol = 2,
  ggplot() + 
    geom_sf(data = chicagoboundary) +
    geom_sf(data = sanitation2, colour = "#41B6E6", size = 0.1, show.legend = "point") +
    labs(title = "Sanitation Code Complaints"), 

  ggplot() + 
  geom_sf(data = chicagoboundary, fill = "#FFFFFF") +
  stat_density2d(data = data.frame(st_coordinates(st_centroid(sanitation2))), 
                 aes(X, Y, fill = ..level.., alpha = ..level..),
                 size = 0.01, bins = 40, geom = 'polygon') +
  scale_fill_distiller(palette = "RdBu") +
  scale_alpha(range = c(0.00, 0.35), guide = FALSE) +
  labs(title = "Density of Sanitation Code Complaints") +
  theme(legend.position = "none"))
```

```{r baiting_visualized, fig.width=9.5, fig.height=4}
grid.arrange(ncol=2,
ggplot() + 
  geom_sf(data = chicagoboundary) +
  geom_sf(data = rodents2, colour="#41B6E6", size=0.1, show.legend = "point") +
  labs(title= "Rodent Baiting"),

ggplot() + 
  geom_sf(data = chicagoboundary, fill = "#FFFFFF") +
  stat_density2d(data = data.frame(st_coordinates(st_centroid(rodents2))), 
                 aes(X, Y, fill = ..level.., alpha = ..level..),
                 size = 0.01, bins = 40, geom = 'polygon') +
  scale_fill_distiller(palette = "RdBu") +
  scale_alpha(range = c(0.00, 0.35), guide = FALSE) +
  labs(title = "Density of Rodent Baiting") + 
  theme(legend.position = "none"))
```

```{r thefts, fig.width=9.5, fig.height=4}
grid.arrange(ncol=2,
ggplot() + 
  geom_sf(data = chicagoboundary) +
  geom_sf(data = thefts, colour="#41B6E6", size=0.1, show.legend = "point") +
  labs(title= "Theft Events"),

ggplot() + 
  geom_sf(data = chicagoboundary, fill = "#FFFFFF") +
  stat_density2d(data = data.frame(st_coordinates(st_centroid(thefts))), 
                 aes(X, Y, fill = ..level.., alpha = ..level..),
                 size = 0.01, bins = 40, geom = 'polygon') +
  scale_fill_distiller(palette = "RdBu") +
  scale_alpha(range = c(0.00, 0.35), guide = FALSE) +
  labs(title = "Density of Theft Events") + 
  theme(legend.position = "none"))
```


Look at 50 nearest points since the point density is so high. 

```{r, nearest_neighboor_analysis, fig.width=9.5, fig.height=4}
# Producing a Nearest Neighbor Analysis Between the 2021 Inspection Data and 2020 Sanitation Complaints and 2020 Rodent Reports

data_2021_2 <- data_2021_2 %>%
    mutate(rodents.nn = nn_function(st_coordinates(data_2021_2), 
                                    st_coordinates(rodents2),
                                           k = 50),
           log_rodents.nn = log(rodents.nn),
           sanitation.nn = nn_function(st_coordinates(data_2021_2), 
                                    st_coordinates(sanitation2),
                                           k = 50),
           log_sanitation.nn = log(sanitation.nn),
          thefts.nn = nn_function(st_coordinates(data_2021_2), 
                                    st_coordinates(thefts),
                                           k = 50),
          log_thefts.nn = log(thefts.nn),
          log_pct_poverty = log(1 + pct_poverty)
           )

my_breaks = c(50,100, 250, 500, 1000, 2000)

grid.arrange(ncol=3,
  
ggplot() +
  geom_sf(data = chicagoboundary, fill = "grey80") +
  geom_sf(data = data_2021_2, aes(color = rodents.nn), size = 0.5) +
  scale_color_viridis_c(name = "distance", trans = "log",breaks = my_breaks, labels = my_breaks)+
  labs(title = "Rodent Complaint") +
  theme_void(),

ggplot() +
  geom_sf(data = chicagoboundary, fill = "grey80") +
  geom_sf(data = data_2021_2, aes(color = sanitation.nn), size = 0.5) +
  scale_color_viridis_c(name = "distance", trans = "log",breaks = my_breaks, labels = my_breaks)+
  labs(title = "Sanitation Complaint") +
  theme_void(),

ggplot() +
  geom_sf(data = chicagoboundary, fill = "grey80") +
  geom_sf(data = data_2021_2, aes(color = thefts.nn), size = 0.5) +
  scale_color_viridis_c(name = "distance", trans = "log",breaks = my_breaks, labels = my_breaks)+
  labs(title = "Thefts") +
  theme_void()
)
```

# Explore Predictors

```{r examine_means,fig.width=10,fig.height=4}

# Look at the means for each continuous predictor

quant_predictors <- c("rodents.nn","sanitation.nn","age","prev_fails","Median_Rent","pct_non_white","pct_poverty","fails_Per_year","thefts.nn")

data_2021_2_means <- data_2021_2 %>%
  st_drop_geometry() %>%
  group_by(results) %>% summarize_at(vars(quant_predictors),mean,na.rm=TRUE) 

data_2021_2_means %>%
  gather(key='variable',value='mean',-results) %>%
  ggplot(aes(x=results,y=mean,fill=results))+
  geom_bar(stat='identity')+
  facet_wrap(~variable,scales = "free",nrow=2)+
  scale_fill_manual(values=c("#E4002B","#41B6E6"),name='Pass Inspection')+
  labs(x="Pass Inspection", y="Mean Value", 
      title = "Feature associations with likelihood of passing inspection")+
  theme_bw()

```

```{r data visualization numeric2, fig.width=14, fig.height=7}

test <- data_2021_2 %>% dplyr::select(quant_predictors,'results') %>% st_drop_geometry() %>%
  gather(key='variable',value='value',-results)

ggplot()+
  geom_density(data=test,aes(x=value,color=results))+
  facet_wrap(~variable,scales = "free")+
  scale_color_manual(values=c("#E4002B","#41B6E6"),name='Enter Housing Subsidy')+
  labs(x="Enter Housing Subsidy Program", y="Density", 
      title = "Feature associations with likelihood of entering housing subsidy program",
      subtitle = "Continous outcomes")+
  theme_bw()

```

```{r table_means}

#"age","prev_fails","Median_Rent","pct_white","pct_poverty","rodents.nn","sanitation.nn","fails_Per_year"

t_age <- t.test(data_2021_2$age~data_2021_2$fail)$p.value
t_prev_fails <- t.test(data_2021_2$prev_fails~data_2021_2$fail)$p.value
t_pct_non_white <- t.test(data_2021_2$pct_non_white~data_2021_2$fail)$p.value
t_pct_poverty <- t.test(data_2021_2$pct_poverty~data_2021_2$fail)$p.value
t_Median_Rent <- t.test(data_2021_2$Median_Rent~data_2021_2$fail)$p.value
t_rodents.nn <- t.test(data_2021_2$rodents.nn~data_2021_2$fail)$p.value
t_sanitation.nn <- t.test(data_2021_2$sanitation.nn~data_2021_2$fail)$p.value
t_fails_per_year <- t.test(data_2021_2$fails_Per_year~data_2021_2$fail)$p.value
t_thefts <- t.test(data_2021_2$thefts~data_2021_2$fail)$p.value

p_values = c(t_age,t_fails_per_year,t_Median_Rent,t_pct_non_white,t_pct_poverty,t_prev_fails,t_rodents.nn,t_sanitation.nn,t_thefts)

data_2021_2_means %>%
  gather('variable','value',-results) %>%
  spread('results','value') %>%
  cbind(.,p_values) %>%
  kbl(col.names=c('Variables','Fail (Mean)','Pass (Mean)','t-test (p-value)')) %>%
  kable_classic_2()
  
```

# Check Correlations

Check correlation between predictors

```{r correlation_matrix}

data_2021_2 %>% dplyr::select(quant_predictors) %>%
  st_drop_geometry() %>%
  correlate() %>% 
  autoplot() +
  geom_text(aes(label = round(r,digits=2)),size = 3)

```


# Modelling

``` {r make_models}
model1 <- glm(fail ~ age + prev_fails + Median_Rent + rodents.nn + sanitation.nn + thefts.nn + pct_poverty,
                     data = data_2021_2,
                     family="binomial" (link="logit"))

summary(model1)
```

``` {r model2}
model2 <- glm(fail ~ age + prev_fails + Median_Rent + log_rodents.nn + log_sanitation.nn + thefts.nn + log_pct_poverty,
                     data = data_2021_2,
                     family="binomial" (link="logit"))

summary(model2)
```


``` {r model3}
model3 <- glm(fail ~ age + prev_fails + Median_Rent + log_rodents.nn + log_sanitation.nn + thefts.nn + risk + pri_neigh + log_pct_poverty,
                     data = data_2021_2,
                     family="binomial" (link="logit"))

summary(model3)
```

``` {r make_predictiosn}
data_2021_2 <- data_2021_2 %>% mutate(probs1 = predict(model1, data_2021_2, type= "response"),
                                      probs2 = predict(model2, data_2021_2, type= "response"),
                                      probs3 = predict(model3, data_2021_2, type= "response"))
```

```{r roc_curve, warning = FALSE, message = FALSE}
ggplot(data_2021_2) +
  geom_roc(aes(d = as.numeric(fail), m = probs1),n.cuts = 50, labels = FALSE, colour = "orange") +
  geom_roc(aes(d = as.numeric(fail), m = probs2),n.cuts = 50, labels = FALSE, colour = "blue") +
  geom_roc(aes(d = as.numeric(fail), m = probs3),n.cuts = 50, labels = FALSE, colour = "red") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1, color = 'grey60') +
  labs(title = "ROC Curve - Housing Subsidy Model")+
  theme_bw()

pred1 <- prediction(data_2021_2$probs1, data_2021_2$fail)
auc1 = performance(pred1, measure ="auc")@y.values[[1]][1]
auc1


pred2 <- prediction(data_2021_2$probs2, data_2021_2$fail)
auc2 = performance(pred2, measure ="auc")@y.values[[1]][1]
auc2

pred3 <- prediction(data_2021_2$probs3, data_2021_2$fail)
auc3 = performance(pred3, measure ="auc")@y.values[[1]][1]
auc3
```

```

